---
title: "Classifications"
author: "Anthony Staines"
date: "`r Sys.Date()`"
output:
  html_document: default
  word_document: default
  pdf_document: 
    toc: true
    fig_caption: true
    number_sections: true
    latex_engine: xelatex
editor_options:
  chunk_output_type: console
bibliography: references.bib
csl: vancouver.csl
---

# Predictions

Prepares predictions for selected outcome variables for the study site file, using the study (chart review) outcomes, and the HIPE predictors.

```{r setup, include=FALSE}
rm(list=ls())

library(tidyverse)
library(lubridate)
library(tibble)
library(tidymodels)
library(readxl)

library(lme4)

library(knitr)
library(kableExtra)
library(summarytools)


library(patchwork)

library(ranger)
library(mlr3verse)
library(mlr3viz)

library(data.table)
library(future)

library(sjPlot)
library(sjtable2df)

library(broom)
library(broom.mixed)

library(stargazer)

library(gt)
library(gtsummary)


tidymodels_prefer(quiet = TRUE)

knitr::opts_chunk$set(echo = FALSE, cache = TRUE, warning = NA, message = NA, fig.pos = 'H',
      cache.extra = knitr::rand_seed)

st_options(ctable.round.digits = 2)
#How many CPU's?
N = 16
  options(Ncpus = N - 1)
  options(mc.cores = N - 1)
  setDTthreads(threads = N - 1,
               restore_after_fork = TRUE,
               throttle = 1024)

options(dplyr.summarise.inform = FALSE, # shut up summarise
        ranger.num.threads = N) # Prepare for rf models
lgr::get_logger("mlr3")$set_threshold("error")
lgr::get_logger("bbotk")$set_threshold("error")


set.seed(979)
rm(N)
```

# Load the merged data file
This is the chart review file merged with the HIPE file provided by HPO.

```{r Load data file}

#####################################################
# Load the merged HIPE/Study data file
# 
Cost2Care.HIPE <- readRDS('data/Cost2Care.HIPE.rds')
NAMES <- read_excel(
      'data/Clean Cost2Care Merged Chart Review and HIPE Data_WORKING.xlsx',
      sheet = 'NAMES')

#####################################################
# Load the total HIPE data file
# 
HIPE <- readRDS('data/HIPE.rds')

```

## Make analysis data file

We give it a shorter typable name 

```{r simplify data}
 
CtCH <- Cost2Care.HIPE
   
HIPE %>% filter(LosC <= 5) %>% summarise( N = n())
ggplot(data = HIPE %>% filter(LosC <= 5),
       aes(x=rawlos)) + geom_boxplot()
```

# Intent

The aim here is to some quick and simple predictions, and summaries


These models can be sense checked by their ability to predict the length of stay, the destination on discharge, and specifically if this was different from the source of admission, and death in hospital.

The most obvious limitation is that the chart review was done in one hospital, a model 4 centre.

A good deal of thought needs to be given to deciding what outcomes to look at - basically the outcome, or the outcome definitely associated with health care.

There are still comments in the PN/PU/UTI/DL_Associated columns  these need to be removed!
Which is the correct F2M variable?

# Outcomes

```{r}

Outcomes <- CtCH |>
  select(PN, PN_Associated, UTI, UTI_Associated, PU, PU_Associated, DL, DL_Associated, rawlos, LosC, Source, Died, Destination)

skimr::skim(Outcomes)

Outcome_recode <- function(DF, COND) {

  ASSOC  <- paste0({{COND}},'_Associated')
  ABBREV <- paste0({{COND}},'_A')

  COND <- ensym(COND)
  ASSOC <- ensym(ASSOC)
  ABBREV <- ensym(ABBREV)

  DF <- DF %>%
  mutate(!!COND := ifelse(is.na(!!COND), 'No', !!COND )) %>% # Missing -> No
  mutate(!!ASSOC := ifelse(is.na(!!ASSOC),'No', !!ASSOC)) %>%
  mutate(!!ASSOC := ifelse(!!ASSOC == 'No' &
                            !!COND == 'No',
                        'Not Applicable',
                        !!ASSOC)) %>%
  mutate(!!ASSOC := case_match(!!ASSOC,
                            'Not Applicable' ~ 'No Dx',
                            'No' ~ 'Unlikely',
                            'LIKELY associated' ~ 'Likely',
                            'DEFINITELY associated.' ~ 'Definite')) %>%
  mutate(!!ABBREV := case_match(!!ASSOC,
                            'No Dx' ~ 'No',
                            'Unlikely' ~ 'No',
                            'Likely' ~ 'Yes',
                            'Definite' ~ 'Yes'
                            ))
return(DF)
}

 DF <- Outcome_recode(Outcomes, 'DL')

 Outcomes <- Outcomes %>%
  Outcome_recode('PN') %>%
  Outcome_recode('UTI') %>%
  Outcome_recode('PU') %>%
  Outcome_recode('DL')

 skimr::skim(Outcomes)
 
CtCH <- CtCH %>%
  Outcome_recode('PN') %>%
  Outcome_recode('UTI') %>%
  Outcome_recode('PU') %>%
  Outcome_recode('DL')
 
```


# Quick and dirty predictions

```{r define tasks}
#################################################
# Trim CtCH, a lot
CCH >- CtCH %>%
  select(StudyID, PN, UTI, PU, UTI, Source, Died, Outcome, LosC,  # Outcomes
         Training, # Derived random split variable
         ModelF, AgeC, SeasonOfAdmission, ScoreEl, ScoreCh, # Variables derived from HIPE
         ProcCount, DxCount, HadxCount, 
         elem, fullelig, drgv.8, 
         ) 
#################################################
# Define a classification task for PN
#
tsk_PN <- as_task_classif(C2C.H %>%
                            select(-c(PN_Associated, PN_A, pneumonia, rawlos)),
                          target = "PN",
                          id = 'PN')
  tsk_PN
  split_PN = partition(tsk_PN)
  
```  
