---
title: "Data load"
author: "Anthony Staines"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  word_document: default
  html_document: default
editor_options:
  chunk_output_type: console
bibliography: references.bib
csl: vancouver.csl
---

```{r setup, include=FALSE}
rm(list=ls())

library(tidyverse)
library(lubridate)
library(tibble)
library(comorbidity)
library(tidymodels)
library(lme4)

tidymodels_prefer(quiet = TRUE)

knitr::opts_chunk$set(echo = FALSE, cache = TRUE,
                      warning = NA, message = NA,
                      fig.pos = 'H',
                      cache.extra = knitr::rand_seed)

N = 16

options(Ncpus = N)
options(ranger.num.threads = N)

set.seed(979)
rm(N)
```

# Load main data file

First we load the data, and then keep 1/5 of the rows for testing, leaving 4/5 for training.

```{r Load main data file, results = 'hide'}
Cost2Care <- as_tibble(read.csv("data/H240272_2022.csv"))

Cost2Care <- Cost2Care %>%
  mutate(rowid_to_column(., var = "ID")) %>% # Numeric ID
  mutate(ID = paste0("ID.",ID, sep = '')) %>% # Character ID
  select(ID, hosp_anon:proc_desc20) %>% # Reorder variables ID first
  mutate(Date_of_admission = paste0('01',mon_adm)) %>% # Process dates in MY format correctly, set day to 1st of each month
  mutate(Date_of_admission = dmy(Date_of_admission))
 
#Then we split
Cost2Care_split <- initial_split(Cost2Care, prop = 4/5, strata = hosp_anon)

# Add a training variable to Attrition

Cost2Care <- Cost2Care %>%
  mutate(Training = FALSE)

# Add a variable to indicate training set or test set.
 Cost2Care$Training[Cost2Care_split$in_id] <- TRUE

#str(DATA, list.len = 200)
# some relevant figures
  PEOPLE <- nrow(Cost2Care)
  HOSPITALS <- length(unique(Cost2Care$hosp_anon))

```

There are a total of `r PEOPLE` admissions in these records, from `r HOSPITALS` different hospitals.

```{r Tidy1}
rm(PEOPLE, HOSPITALS)
```

The next step is to create a number of additional variables required for analysis and data display. These mostly consist of a re-ordering of the 'model' variable, which indicates the type of hospital (Model 4, Model 3 Model 2, Specialist, or Maternity) and the creation of hospital ID's which number the hospitals within these groups.

```{r add variables here}
Cost2Care <- Cost2Care %>%
    # Now we reorder the group
    mutate(MODELX = as_factor(model)) %>%
    mutate(modelF = fct_relevel(
        MODELX,
        c("Model 4", "Model 3", "Model 2", "Specialist", "Maternity" ),
        after = Inf)) %>%
    select (-MODELX) %>%
    # now we identify the group
    mutate(ModelCode = case_match(model,
        'Model 4' ~ '4',
        'Model 3' ~ '3',
        'Model 2' ~ '2',
        'Specialist' ~ 'S',
        'Maternity' ~ 'M'
    ))

#Make short per hospital codes
CODES <- Cost2Care %>%
    select(ModelCode, hosp_anon) %>%
    group_by(ModelCode) %>% 
    arrange(ModelCode, hosp_anon) %>%
    distinct() %>%
    mutate(HospNo = row_number()) %>%
    mutate(HospCode = paste0(ModelCode, '.', HospNo)) %>%
    mutate(HospCode = fct_inorder(HospCode))

# Merge the short codes back into the main dataset

Cost2Care <- Cost2Care %>%
    left_join(CODES, by = join_by(hosp_anon, ModelCode))

rm(CODES)
```
Although some of the admissions were a very long time before discharge, most occurred during late 2021 and  2022, as Figure 1 shows.

```{r Admission dates by time, fig.cap= 'Admission dates by month and year for discharges included in the analysis.', fig.dpi=600, fig.height=4, fig.width=6}
Admissions <- Cost2Care %>%
    group_by(Date_of_admission) %>%
    summarise(N = n())

ggplot(data=Admissions,
       aes(x=Date_of_admission, y= N)) +
           geom_point(colour = 'red',
                      size = 3) +
    scale_x_date(date_breaks = '6 months',
                 date_labels = '%b_%y') +
           labs( title = 'Admissions per month in data set',
                 subtitle = 'HIPE data, aged 65 years or over, 3 or more days stay, acute hospitals only',
                 x = 'Date of admission',
                 y = 'Count') +
    theme_minimal(base_size = 12)
       
rm(Admissions)
```

## Length of stay

Lengths of stay varied greatly also, as Figure 2 shows. Model of hospital was one important source of variation, but between hospitals there is also evidence of considerable variation. In part, this is to be expected, given the differing roles of Model 4, Model 3, and Model 2 hospitals.

```{r Length of stay by hospital and hospital type, fig.cap= 'Admission dates by month and year for discharges included in the analysis.', fig.dpi=1200, fig.height=5, fig.width=7}


ggplot(data=Cost2Care,
       aes(x=HospCode, y = Rawlos, colour = modelF)) +
           geom_boxplot(outliers = FALSE, varwidth = TRUE) +
  scale_x_discrete(guide = guide_axis(angle = 90)) +
    facet_wrap(~modelF, scales = 'free') +
           labs( title = 'Length of stay in days by hospital model and site\n (outliers excluded)',
                 subtitle = 'HIPE data, aged 65 years or over, 3 or more days stay, acute hospitals only',
                 x = 'Hospital code',
                 y = 'Count') +
  guides(colour = guide_legend("Hospital\nModel"),
         fill = guide_legend("Hospital\nModel")) +
    theme_minimal(base_size = 12)

```

A table showing the median, and a range of quantiles for the length of stay is also helpful. This is presented in the same order as the items in Figure 2.

```{r LOS Table}

LOS <- Cost2Care %>%
    group_by(modelF, HospCode) %>%
    summarise(Mean = round(mean(Rawlos, na.rm = TRUE),2),
              Median = median(Rawlos, na.rm = TRUE),
              Q00 = min(Rawlos, na.rm = TRUE),
              Q10 = quantile(Rawlos, probs = 0.1),
              Q25 = quantile(Rawlos, probs = 0.25),
              Q50 = quantile(Rawlos, probs = 0.5),
              Q75 = quantile(Rawlos, probs = 0.75),
              Q90 = quantile(Rawlos, probs = 0.90)) %>%
    ungroup()

kbl(LOS,  booktabs = TRUE, longtable = TRUE,
    caption = "Length of Stay by Hospital Type and Site.")

rm(LOS)
```

Again there is substantial variation between and within hospital types.

Quantifying this variability we can use a random effects regression model. This allows the analysis of the effects of hospital type and other variables (fixed effects) and the variability between individual hospitals (random effects).

```{r Regression}

Model1 <- lmer(data=Cost2Care,
             Rawlos ~ modelF + age + sex +
               (1 + HospCode | mdc))

Model1
insight::model_info(Model1)

sjPlot::tab_model(Model1)
```
# Comorbidity scores

It can be useful to consider comorbidity scores, and two of the most popular of these are the Elixhauser  and Charlson  scores. These are calculated using in this work using the comorbidity package , in turn based on.

```{r Scoring}
#Data %>% unite("ICD_combined", dx01:dx30, sep=', ', na.rm=TRUE)
Data <- Data %>%
  unite("ICD_combined", dx01:dx30, sep=' ',
        remove = FALSE, na.rm=TRUE)
charlson <- comorbidity(x = Data, id = "ID", code = "ICD_combined", map = "charlson_icd10_am", assign0 = FALSE)
    charlson <- charlson %>% 
      mutate(score = score(charlson, weights='quan', assign0 = TRUE))
        names(charlson)[-1] <- paste0(names(charlson)[-1], '.Ch', sep='')

elixhauser <- comorbidity(x = Data, id = "ID", code = "ICD_combined", map = "elixhauser_icd10_quan", assign0 = FALSE)
    elixhauser <- elixhauser %>% 
      mutate(score = score(elixhauser, weights='swiss', assign0 = TRUE))
        names(elixhauser)[-1] <- paste0(names(elixhauser)[-1], '.El', sep='')
        
    
Data <- Data %>%
  left_join(charlson, by = join_by(ID), suffix = c("", ".ch")) %>%
  left_join(elixhauser, by = join_by(ID),suffix = c("", ".el"))

rm(charlson, elixhauser)
```

Figure 3 shows the joint and separate distributions of these scores amongst the discharges.  The very limited range of Charlson scores encountered, is contrasted with the much wider range of the Elixhauser scores.

```{r Plot of E & C scores, fig.cap= 'Plot of Elixhauser and Charlson weighted scores for the discharges included in the analysis.', fig.dpi=1200, fig.height=5, fig.width=7}
ggplot(data=Data,
       aes(x = score.Ch, y = score.El,
           fill = ModelCode, colour = ModelCode)) +
  geom_tile() +
  facet_wrap(~ModelCode) +
           labs( title = 'Plot of Elixhauser and Charlson weighted scores',
                 subtitle = 'HIPE data, aged 65 years or over, 3 or more days stay, acute hospitals only',
                 x = 'Charlson Score',
                 y = 'Elixhauser Score') +
  guides(colour = guide_legend("Hospital\nModel"),
         fill = guide_legend("Hospital\nModel")) +
    theme_minimal(base_size = 12)
```

# Impact of scores


# Bibliography


