---
title: "Data load"
author: "Anthony Staines"
date: "`r Sys.Date()`"
output:
  pdf_document: 
    toc: true
    fig_caption: true
    number_sections: true
    latex_engine: xelatex
  word_document: default
  html_document: default
editor_options:
  chunk_output_type: console
bibliography: references.bib
csl: vancouver.csl
---

```{r setup, include=FALSE}
rm(list=ls())

library(tidyverse)
library(lubridate)
library(tibble)
library(readxl)

library(skimr)
library(gt)

library(comorbidity)
library(tidymodels)
library(lme4)
#library(lmerTest)
library(knitr)
library(kableExtra)

library(sjPlot)
library(sjtable2df)
library(broom)
library(broom.mixed)
library(summarytools)

library(pixiedust)
library(stargazer)

tidymodels_prefer(quiet = TRUE)

knitr::opts_chunk$set(echo = FALSE, cache = TRUE,
                      warning = NA, message = NA,
                      fig.pos = 'H',
                      cache.extra = knitr::rand_seed)
N = 16

options(Ncpus = N)
options(mc.cores = N)
options(dplyr.summarise.inform = FALSE, # shut up summarise
        ranger.num.threads = N) # Prepare for rf models

lgr::get_logger("mlr3")$set_threshold("error")
lgr::get_logger("bbotk")$set_threshold("error")

set.seed(979)
rm(N)
```

# Aims

This file loads the main HIPE data, and the HIPE data for the study hospital, a Model 4 hospital, the chart review data for the study hospital, and a file of the ACHI procedure codes used nationally in that year. It processes these data, and prepares the analysis datasets.

# Load main HIPE ACHI and Chart Review data files

First we load the data.

```{r Load main data files, results = 'hide'}
HIPE <- as_tibble(read.csv("data/H240272_2022.csv",
        strip.white = TRUE, na.strings = c("", NA)))

###################################################
#There is a StudyID variable at the start of the HIPE site file, so we add a blank StudyID to the start of this HIPE file
#
HIPE <- HIPE %>%
  mutate(StudyID = 0)

###################################################
# Hipe linked to chart review file
# 
HIPE.Site <- as_tibble(
  read.csv("data/H240272_2022_Site_Study_Subjects.csv", strip.white = TRUE, na.strings = c("", NA)))

#####################################################
# Check the sheet names (Note the extra ' ' in the "Chart review data ")
# 
excel_sheets('data/Final Cleaned Data Cost2Care Chart Review and HIPE Data 17th February 2025 WORKING.xlsx')

Cost2Care <- read_excel(path='data/Clean Cost2Care Merged Chart Review and HIPE Data_WORKING.xlsx',
                        sheet = 'Chart review data ',
                        range = "A2:FX1002")

#####################################################
# Fix the names
# PN - PNeumonia;       UTI - Urinary Tract Infection;
# PU - Pressure Ulcer;  DL - DeLirium
# 
    NAMES <- read_excel(
      'data/Final Cleaned Data Cost2Care Chart Review and HIPE Data 17th February 2025 WORKING.xlsx',
      sheet = 'NAMES')
          names(Cost2Care) <- NAMES$Chart_review_data_revised

#####################################################
# Remove 5 empty columns with missing names
# 
Cost2Care <- Cost2Care %>%
  select(-c(which(is.na(names(Cost2Care)))))

###################################################
# ACHI file
# 
excel_sheets('data/H240272_Proc_ACHI_MAP_10thEdn.xlsx')

ACHI <- as_tibble(
  read_excel('data/H240272_Proc_ACHI_MAP_10thEdn.xlsx',
             sheet = 'Proc_ACHI_MAP_10thEdn'))
```

## Process the HIPE data

We now have the four original data files loaded, and minimally tidied.
We now do a *lot* more preparation on the national and site HIPE data files.

We write a function that
* Names the variables consistently
* Generates a number of new variables
    + ID, a unique identifier variable
    + DateOfAdmission, DateOfDischarge, MonthOfAdmission, MonthOfDischarge
    + SeasonOfAdmission (Nov-Feb = Winter) (Mar-Oct = Other)
    + MedSurg, based on recorded specialty on admission
    + ModelF, a factor for Hospital Model
    + HospNo and HospCode
    + Source - four levels each, Home, Care, Transfer, Other
    + Destination - four levels each, Home, Care, Transfer, Dead, Other
    + Died - Dead or Alive
    + Charlson and Elixhauser scores and components
    + ProcCount, HadxCount, and DxCount - counts of non-missing codes
    + AgeC and LosC - centred and scaled Age (age) and Length of stay (rawlos)

```{r Function <HIPE_PROCESS> to process both HIPE files}
HIPE_PROCESS <- function (HIPE_FILE) {
#############################################
# tidy up the names in the files provided
# 
  names(HIPE_FILE)
    names(HIPE_FILE) <- str_to_lower(names(HIPE_FILE)) # All lower case
    names(HIPE_FILE) <- str_replace_all(names(HIPE_FILE), "_", ".") # no _, use . instead
    names(HIPE_FILE) <- str_replace(names(HIPE_FILE), "(\\d*$)", ".\\1") # A dot place before any digits at the end, otherwise at the end
    names(HIPE_FILE) <- str_replace(names(HIPE_FILE), "(\\.$)", "") # Remove unwanted dots at the end, those not followed by digits.

#############################################
# Set up an ID variable
#   
HIPE_FILE <- HIPE_FILE %>%
  mutate(rowid_to_column(., var = "ID")) %>% # Numeric ID
  mutate(ID = paste0("ID.",ID, sep = '')) # Character ID

#############################################
# Calculate some time related variables
# 
HIPE_FILE <- HIPE_FILE %>%
  mutate(DateOfAdmission = paste0('15',mon.adm)) %>% # Process dates in MY format correctly, set day to 15th of each month
  mutate(DateOfAdmission = dmy(DateOfAdmission)) %>%
  mutate(DateOfDischarge = (DateOfAdmission + rawlos)) %>% # Crude estimate of date of discharge, but all we want is winter/not_winter
  mutate(MonthOfAdmission = lubridate::month(DateOfAdmission, label=TRUE)) %>%
  mutate(MonthOfDischarge = lubridate::month(DateOfDischarge, label=TRUE)) %>%
  mutate(SeasonOfAdmission =
           case_match(MonthOfAdmission,
                      c("Nov","Dec","Jan", "Feb") ~ "Winter",
c("Mar","Apr","May","Jun","Jul","Aug","Sep","Oct") ~ "Other"
                                    ))
#############################################
# Prepare a Medical/Surgical Group variable
# REPLACE WHEN PROCEDURE CODES FOR ANAESTHETICS AVAILABLE!!
HIPE_FILE <- HIPE_FILE %>%
      mutate(MedSurg = 
                case_match(specialty,
"Accident & Emergency" ~ "Medical",
"Cardiology" ~ "Medical",
"Clinical (Medical) Genetics" ~ "Medical",
"Dermatology" ~ "Medical",
"Diabetes Mellitus" ~ "Medical",
"Endocrinology" ~ "Medical",
"Gastro-Enterology" ~ "Medical",
"General Medicine" ~ "Medical",
"Genito-Urinary Medicine" ~ "Medical",
"Geriatric-Medicine" ~ "Medical",
"Haematology" ~ "Medical",
"Histopathology" ~ "Medical",
"Infectious Diseases" ~ "Medical",
"Intensive Care" ~ "Medical",
"Microbiology" ~ "Medical",
"Nephrology" ~ "Medical",
"Neurology" ~ "Medical",
"Neuroradiology" ~ "Medical",
"Oncology" ~ "Medical",
"Paediatric Oncology" ~ "Medical",
"Paediatrics" ~ "Medical",
"Pain Relief" ~ "Medical",
"Palliative Medicine" ~ "Medical",
"Psychiatry" ~ "Medical",
"Radiology" ~ "Medical",
"Radiotherapy" ~ "Medical",
"Respiratory Medicine" ~ "Medical",
"Rheumatology" ~ "Medical",
"Anaesthetics" ~ "Surgical",
"Breast Surgery" ~ "Surgical",
"Cardio-Thoracic Surgery" ~ "Surgical",
"Dental Surgery" ~ "Surgical",
"Gastro-Intestinal Surgery" ~ "Surgical",
"General Surgery" ~ "Surgical",
"Gynaecology" ~ "Surgical",
"Hepato-Biliary Surgery" ~ "Surgical",
"Maxillo-Facial" ~ "Surgical",
"Neurosurgery" ~ "Surgical",
"Obstetrics" ~ "Surgical",
"Obstetrics/Gynaecology" ~ "Surgical",
"Ophthalmology" ~ "Surgical",
"Orthopaedics" ~ "Surgical",
"Otolaryngology (ENT)" ~ "Surgical",
"Plastic Surgery" ~ "Surgical",
"Renal Transplantation" ~ "Surgical",
"Urology" ~ "Surgical",
"Vascular Surgery" ~ "Surgical"))
             
#############################################
# Then we split into training and test datasets
# 
HIPE_FILE_split <- initial_split(HIPE_FILE, prop = 4/5, strata = hosp.anon)

# Add a training variable to the dataframe

HIPE_FILE <- HIPE_FILE %>%
  mutate(Training = FALSE)

# Add a variable to indicate training set or test set.
 HIPE_FILE$Training[HIPE_FILE_split$in_id] <- TRUE

#############################################
# Add Hospital Model codes
HIPE_FILE <- HIPE_FILE %>%
    # Now we reorder the group
    mutate(MODELX = as_factor(model)) %>%
    mutate(ModelF = fct_relevel(
        MODELX,
        c("Model 4", "Model 3", "Model 2", "Specialist", "Maternity" ),
        after = Inf)) %>%
    select (-MODELX) %>%
    # now we identify the group
    mutate(ModelCode = case_match(model,
        'Model 4' ~ '4',
        'Model 3' ~ '3',
        'Model 2' ~ '2',
        'Specialist' ~ 'S',
        'Maternity' ~ 'M'
    ))

#############################################
# Make short per hospital codes
CODES <- HIPE_FILE %>%
    select(ModelCode, hosp.anon) %>%
    group_by(ModelCode) %>% 
    arrange(ModelCode, hosp.anon) %>%
    distinct() %>%
    mutate(HospNo = row_number()) %>%
    mutate(HospCode = paste0(ModelCode, '.', HospNo)) %>%
    mutate(HospCode = fct_inorder(HospCode))

# Merge the short codes back into the main dataset

HIPE_FILE <- HIPE_FILE %>%
    left_join(CODES, by = join_by(hosp.anon, ModelCode))

#############################################
# Sensibly code Source and Destination
# 
# 
HIPE_FILE <- HIPE_FILE %>%
    mutate(Source = case_match(source,
                            1 ~ "Home",
                            2 ~ "Care",
                            3 ~ "Transfer",
                            c(0,4,5,6,7,8,9) ~ "Other")) %>%
    mutate(Died = case_match(discode,
                            c(6,7) ~ "Dead",
                            c(0,1,2,3,4,5,
                              8,9,10,11,
                              12,13,14,15) ~ "Alive")) %>%
    mutate(Destination = case_match(discode,
                            1 ~ "Home",
                            c(2,11) ~ "Care", # includes hospice
                            c(3,4,5,8,9,10) ~ "Transfer",
                            c(6,7) ~ "Dead",
                            c(0,12,13,14,15) ~ "Other"))

#############################################
# Scoring - Calculate Elixhauser and Charlson codes
# 
HIPE_FILE <- HIPE_FILE %>%
  unite("ICD_combined", dx.01:dx.30, sep=' ',
        remove = FALSE, na.rm=TRUE) # comorbidity expects a single variable containing all the ICD10 codes to be used as a a string, hence ICD-combined - This is a *BAD* idea.

#############################################
# Charlson
charlson <- comorbidity(x = HIPE_FILE, id = "ID", code = "ICD_combined", map = "charlson_icd10_am", assign0 = FALSE)
    charlson <- charlson %>% 
      mutate(score = score(charlson, weights='quan', assign0 = TRUE))
        names(charlson)[-1] <- paste0(str_to_title(names(charlson)[-1]),
                                      'Ch', sep='')

#############################################
# Elixhauser
elixhauser <- comorbidity(x = HIPE_FILE, id = "ID", code = "ICD_combined", map = "elixhauser_icd10_quan", assign0 = FALSE)
    elixhauser <- elixhauser %>% 
      mutate(score = score(elixhauser, weights='swiss', assign0 = TRUE))
        names(elixhauser)[-1] <- paste0(str_to_title(names(elixhauser)[-1]),
                                        'El', sep='')

#############################################
# Put the scores back in the main file
HIPE_FILE <- HIPE_FILE %>%
  left_join(charlson, by = join_by(ID), suffix = c("", ".ch")) %>%
  left_join(elixhauser, by = join_by(ID),suffix = c("", ".el"))

#############################################
# Ad a count of procedures, diagnoses and hadx scores
# 
HIPE_FILE <- HIPE_FILE %>%
  mutate(ProcCount = purrr::pmap_dbl(HIPE_FILE %>% select(proc.01:proc.20),
                           ~sum(!is.na(c(...))))) %>%
  mutate(DxCount = purrr::pmap_dbl(HIPE_FILE %>% select(dx.01:dx.30),
                           ~sum(!is.na(c(...))))) %>%
  mutate(HadxCount = purrr::pmap_dbl(HIPE_FILE %>% select(hadx.01:hadx.30),
                           ~sum(!is.na(c(...)))))

#############################################
# Centre and scale age, rawlos and other numeric variables
# 
HIPE_FILE <- HIPE_FILE %>%
  mutate(AgeC = as.vector(scale(age))) %>%
  mutate(LosC = as.vector(scale(rawlos)))

#
## scale produces a matrix output
#

#############################################
# Select and order the desired variables
# This will *change* if more calculated variables are added
# 
HIPE_FILE <- HIPE_FILE %>%
  mutate(StudyID = studyid) %>% #Capitalise this again
  select(StudyID, ID, Training, ModelF, ModelCode, HospCode, MedSurg,
         AgeC, LosC,
         DateOfAdmission, MonthOfAdmission, SeasonOfAdmission,
         DateOfDischarge, MonthOfDischarge,
         ScoreEl, ScoreCh, HospNo:Destination, ProcCount:HadxCount,
         hosp.anon:proc.desc.20) # Reorder variables

#############################################
# Finish, returning a single tibble
#
    return(HIPE_FILE)
}

```

```{r Process both files HIPE and HIPE.Site}

HIPE <- HIPE_PROCESS(HIPE)
HIPE.Site <- HIPE_PROCESS(HIPE.Site)
```

Next we check and merge the Chart Review data, and the corresponding HIPE data for those cases.

```{r Check and merge two sets of site data}

#####################################################
# Note there are 2 StudyIDs 41 and 405 which are 
# not in the Cost2Care file, but are in the HIPE.Site file
# This is correct.
# 
COMBINED <- full_join(
  Cost2Care %>%
    select(StudyID, Encrypted_mrn),
  HIPE.Site %>%
    select(StudyID, ID),
      by = join_by(StudyID)) # check for missing study IDS

#####################################################
# Join the main files
# Lose the two rows with no Encrypted_mrn - StudyID's 41 and 405
# 
Cost2Care.HIPE <- full_join(
    Cost2Care,
    HIPE.Site,
    by = join_by(StudyID)) %>%
  filter(!is.na(Encrypted_mrn))

##################################################
# Duplicate names - fixed in Cost2Care working spreadsheet sheet NAMES
# 'data/Final Cleaned Data Cost2Care Chart Review and HIPE Data 17th February 2025 WORKING.xlsx'
# 
NN <- names(Cost2Care.HIPE)
NN[c(which(str_detect(NN, "\\.y|\\.x")))] # Should be PN.xray only
rm(COMBINED, NAMES, NN)
```

## Summary report

```{r Calculate some useful numbers}
# some relevant figures
  PEOPLE <- nrow(HIPE)
  HOSPITALS <- length(unique(HIPE$hosp.anon))
  STUDY <- nrow(HIPE.Site)

```

There are a total of `r PEOPLE` admissions in these records, from `r HOSPITALS` different hospitals. Of these `r STUDY` from one Model 4 hospital took part in the chart review study.

```{r Delete the numbers}
rm(PEOPLE, HOSPITALS, STUDY)
```

## Process the procedures data

For the diagnoses, there are two sets of summary codes already provided. These are DRG codes and MDC codes, which provide, respectively, a longer and shorter summary of the diagnosis assigned. For procedures no simple classification is accessible. Each person has up to 30 codes, and the only guide is the the first procedure is that associated with the reason for admission. After that, many of the procedure codes are blank, as most people have less than 3 procedure codes.

### Intent of processing procedure codes

We have two goals - 

* Identify people who had anaesthetics, often used as a proxy for surgical cases.
* Reduce the number of procedure codes to a manageable number for further analysis.

To do this we have access to the following for each of the procedures used in the data -
* proc - One of 2,469 numeric procedure codes
* proc_desc - A description of what each code covers
* Block -  One of 942 numeric codes for an aggregate of related procedure codes
* block_desc - A description of each block
* Proc_Type - One of 81 general descriptions of the type of procedure
* Anatomical_Site - One of 119 body sites where that procedure was done
* Chapter_n - One of 19 codes for the ACHI chapter into which that procedure falls
* Chapter - A description of each chapter

```{r}
skim(ACHI %>%
       mutate( across( where(is.numeric) , as.character)))
```

### Task 1
How to add ACHI codes to the main dataset.

Simplify data to ID and proc codes

```{r}
PROC <- Cost2Care.HIPE |>
  select(StudyID,proc.01:proc.20) |>
  pivot_longer(cols=!StudyID,
               names_to = 'Procedure',
               values_to = 'ACHI_code')
PROC <- PROC |>
  full_join(ACHI, by = join_by(ACHI_code == proc))

    PROC_unused <- PROC |> filter(is.na(StudyID)) |> select(ACHI_code) |>
      group_by(ACHI_code) |> unique() |>
      arrange(ACHI_code) # 1998 codes not used
    PROC_used <- PROC |> filter(!is.na(StudyID)) |> select(ACHI_code) |>
      group_by(ACHI_code) |> unique() |>
      arrange(ACHI_code) # 472 codes used
# Total codes is 2470 - the original 2469 and the missing code
# Drop the 1998 unused codes from PROC for simplicity
PROC <- PROC |> filter(!is.na(StudyID)) 


# Doesn't work, 1 row per procedure observation, per person - total of 5393
#PROC2 <- PROC |> pivot_wider(names_from = Procedure, values_from = ACHI_code)

```

```{r Anaesthetic code}

```
```{r function <PROC_Process> to recode procedures}
##################################
# Each person can have up to 20 ACHI procedure codes
# There is no particular rationale to the ordering of the codes, and it is not meaningful
# The aim here is to generate a set of variables indicating for each person which group of codes they have
#


HIPE.Site.ACHI <- HIPE.Site %>%
  pivot_longer(cols = proc.01:proc.20,
               names_to = 'Procedures',
               values_to = 'Code'
               ) %>%
  left_join(ACHI,
            by = join_by(Code == proc)
            ) %>%
  pivot_wider(id_cols = c(StudyID:ID,Block:Chapter),
              id_expand = FALSE,
              names_from = 'Procedures',
              values_from = 'Code')

HIPE.Site.ACHI %>%
  group_by(Chapter) %>%
  summarise(N = n()) %>%
  arrange(desc(N))

HIPE.Site.ACHI %>%
  group_by(Proc_Type) %>%
  summarise(N = n()) %>%
  arrange(desc(N)) %>%
  print(n = 50)

HIPE.Site.ACHI %>%
  group_by(Chapter,Proc_Type) %>%
  summarise(N = n()) %>%
  arrange(desc(N)) %>%
  print(n = 90)

```

The next step is to create a number of additional variables required for analysis and data display. These mostly consist of a re-ordering of the 'model' variable, which indicates the type of hospital (Model 4, Model 3 Model 2, Specialist, or Maternity) and the creation of hospital ID's which number the hospitals within these groups.



# Outcomes

## Timing of admissions

Although some of the admissions were a very long time before discharge, most occurred during late 2021 and  2022, as Figure 1 shows.

```{r Admission dates by time, fig.cap= 'Admission dates by month and year for discharges included in the analysis.', fig.dpi=600, fig.height=4, fig.width=6}
Admissions <- HIPE %>%
    group_by(DateOfAdmission) %>%
    summarise(N = n())

ggplot(data=Admissions,
       aes(x=DateOfAdmission, y= N)) +
           geom_point(colour = 'red',
                      size = 3) +
    scale_x_date(date_breaks = '6 months',
                 date_labels = '%b_%y') +
           labs( title = 'Admissions per month in data set',
                 subtitle = 'HIPE data, aged 65 years or over, 3 or more days stay, acute hospitals only',
                 x = 'Date of admission',
                 y = 'Count') +
    theme_minimal(base_size = 12)
       
rm(Admissions)
```

## Comorbidity scores

It can be useful to consider comorbidity scores, and two of the most popular of these are the Elixhauser  and Charlson  scores. These are calculated using in this work using the comorbidity package , in turn based on.

Figure 3 shows the joint and separate distributions of these scores amongst the discharges.  The very limited range of Charlson scores encountered, is contrasted with the much wider range of the Elixhauser scores.

```{r Plot of E & C scores, fig.cap= 'Plot of Elixhauser and Charlson weighted scores for the discharges included in the analysis.', fig.dpi=1200, fig.height=5, fig.width=7}
ggplot(data=HIPE,
       aes(x = ScoreCh, y = ScoreEl,
           fill = ModelCode, colour = ModelCode)) +
  geom_tile() +
  facet_wrap(~ModelCode) +
           labs( title = 'Plot of Elixhauser and Charlson weighted scores',
                 subtitle = 'HIPE data, aged 65 years or over, 3 or more days stay, acute hospitals only',
                 x = 'Charlson Score',
                 y = 'Elixhauser Score') +
  guides(colour = guide_legend("Hospital\nModel"),
         fill = guide_legend("Hospital\nModel")) +
    theme_minimal(base_size = 12)
```

## Length of stay

Lengths of stay varied greatly also, as Figure 2 shows. Model of hospital was one important source of variation, but between hospitals there is also evidence of considerable variation. In part, this is to be expected, given the differing roles of Model 4, Model 3, and Model 2 hospitals.

```{r Length of stay by hospital and hospital type, fig.cap= 'Length of stay (days) by hospital model and site (outliers excluded).', fig.dpi=1200, fig.height=5, fig.width=7}


ggplot(data=HIPE,
       aes(x=HospCode, y = rawlos, colour = ModelF)) +
           geom_boxplot(outliers = FALSE, varwidth = TRUE) +
  scale_x_discrete(guide = guide_axis(angle = 90)) +
    facet_wrap(~ModelF, scales = 'free') +
           labs( title = 'Length of stay in days by hospital model and site\n (outliers excluded)',
                 subtitle = 'HIPE data, aged 65 years or over, 3 or more days stay, acute hospitals only',
                 x = 'Hospital code',
                 y = 'Count') +
  guides(colour = "none", fill = "none", size = "none") +
  #guides(colour = guide_legend("Hospital\nModel"),
  #       fill = guide_legend("Hospital\nModel")) +
    theme_minimal(base_size = 12)

```

A table showing the median, and a range of quantiles for the length of stay is also helpful. This is presented in the same order as the items in Figure 2.

```{r LOS Table}

LOS <- HIPE %>%
    group_by(ModelF, HospCode) %>%
    summarise(Mean   = round(mean(rawlos, na.rm = TRUE),2),
              Q10    = quantile(rawlos, probs = 0.1),
              Q25    = quantile(rawlos, probs = 0.25),
              Median = quantile(rawlos, probs = 0.5),
              Q75    = quantile(rawlos, probs = 0.75),
              Q90    = quantile(rawlos, probs = 0.90)) %>%
    ungroup()

kbl(LOS,  booktabs = TRUE, longtable = TRUE,
    caption = "Length of Stay by Hospital Type and Site.")

rm(LOS)
```

Again there is substantial variation between and within hospital types.

## Deaths, and discharge outcomes

Another very important variable is deaths in hospital. While most patients are discharged alive (be that a return home, or a transfer to other care sites, including other acute hospitals), about 6% of those admitted, aged over 65, and staying for more than three days, did not survive.

The table gives the overall results, and the figure shows how this varied between hospitals, and hospital types

```{r Dead table}
Dead <- HIPE %>%
  group_by(Died) %>%
  summarise(N = n())

kbl(Dead,  booktabs = TRUE, longtable = FALSE,
    caption = "Discharged alive or dead.")

rm(Dead)
```


```{r Risk of death by hospital and hospital type, fig.cap= 'Risk of death (per person) by hospital model and site.', fig.dpi=1200, fig.height=5, fig.width=7}
Dead <- HIPE %>%
  select(ModelF, HospCode, Died) %>%
  group_by(ModelF, HospCode, Died) %>%
  summarise(N = n()) %>%
  pivot_wider(names_from = Died, values_from = N) %>%
  ungroup() %>%
  mutate(Dead = ifelse(is.na(Dead), 0, Dead)) %>%
  mutate(Admissions = Alive+Dead) %>%
  mutate(Risk = Dead/(Admissions))

ggplot(data=Dead,
       aes(x=HospCode, y = Risk, colour = ModelF)) +
           geom_point(aes(size = Admissions)) +
  scale_x_discrete(guide = guide_axis(angle = 90)) +
    facet_wrap(~ModelF, scales = 'free_x') +
           labs( title = 'Risk of death by hospital model and site\n (point size is number of Admissions)',
                 subtitle = 'HIPE data, aged 65 years or over, 3 or more days stay, acute hospitals only',
                 x = 'Hospital code',
                 y = 'Risk of death') +
  guides(colour = "none", fill = "none", size = "none") +
    theme_minimal(base_size = 12)

rm(Dead)
```

It is important to emphasise that these crude death rates cannot be used to measure hospital outcomes, and still less to engage in the dubious activity of preparing league tables. Having said that, the results are not very surprising, and reflect the different roles and patient populations of the hospitals involved.

## Hospital coding

Different hospitals will provide different bundles of care. This is partly captured in the Hospital model. They may also have different coding practices. The coders receive common training, but the materials form they which they code may be more variable. To begin to address this, we start by examining the number of codes used in each hospital.

```{r Calculate code counts}
Coding_Summary <- HIPE %>% group_by(ModelF,HospCode) %>% summarise(across(c(age, ProcCount:HadxCount, ScoreEl), list(median = median, mean = mean, sd = sd)))
```

We show a series of hospital level variables.

### Age

Age at admission does not vary greatly between the main group of hospitals. This work is confined to an older group of patients, all aged 65 or over, and admitted for at least three days.

```{r Draw age}
ggplot(data = HIPE,
       aes(x = HospCode, y = age, colour = ModelF)) +
  geom_jitter(alpha = 0.05) +
  geom_violin() +
  facet_wrap(~ModelF, scales='free_x') +
  labs (title='Age',
        x = 'Hospital',
        y = 'Age (years)')
```

### Elixhauser score

All hospitals have a wide range of Elixhauser scores, but Model 4 hospitals have more of the highest scores than the others. The commonest score is zero. Neither of these is unexpected.

```{r ScoreEl}
ggplot(data = HIPE,
       aes(x = HospCode, y = ScoreEl, colour = ModelF)) +
  geom_jitter(alpha = 0.05) +
  geom_violin() +
  facet_wrap(~ModelF, scales='free_x') +
  labs (title='Elixhauser score',
        x = 'Hospital',
        y = 'Elixhauser score')
```

### Counts of codes given

Each discharge record has up to three sets of codes - a code for up to thirty diagnoses, a code for up to twenty procedures, and a code for up to thirty health care acquired diagnoses.

For diagnoses, there is considerable variability in the number of codes given, which partly reflects case mix, and partly coding practices.

```{r Diagnosis codes count}
ggplot(data = HIPE,
       aes(x = HospCode, y = DxCount, colour = ModelF)) +
  geom_jitter(alpha = 0.05) +
  geom_boxplot() +
  facet_wrap(~ModelF, scales='free_x') +
  labs (title='Number of diagnoses coded',
        x = 'Hospital',
        y = 'Number of Diagnoses coded')
```

A similar pattern can be seen for procedures, although there is some suggestions that practices in individual hospitals may be rather more different.

```{r Procedure codes count}
ggplot(data = HIPE,
       aes(x = HospCode, y = ProcCount, colour = ModelF)) +
  geom_jitter(alpha = 0.05) +
  geom_violin() +
  facet_wrap(~ModelF, scales='free_x') +
  labs (title='Number of procedures coded',
        x = 'Hospital',
        y = 'Number of Procedures coded')
```

For health care acquired diagnoses the median number of codes given is 0 in every hospital. The mean ranges from just over 0 to just over 2 depending on the hospitals, though there is substantial variability.

```{r HADx codes count}
ggplot(data = HIPE,
       aes(x = HospCode, y = HadxCount, colour = ModelF)) +
  geom_jitter(alpha = 0.05) +
  geom_boxplot() +
  facet_wrap(~ModelF, scales='free_x') +
  labs (title='Number of health care acquired diagnoses coded',
        x = 'Hospital',
        y = 'Number of Health care Acquired Diagnoses coded')
```


# Checking of the Chart Review data and the HIPE site data


## Check dataset and check matching

First, we produce two summaries of the dataset. Please review these, and be sure that they are correct.

## skimr

```{r Check data skimr, results = 'asis'}
skimr::skim(Cost2Care.HIPE)
```


## Check matching

It is desirable to check the matching, and see if the other HIPE.Site variables have the same values as those in the Cost2Care file.

There are two groups for comparison. 

## HIPE

In the first group the codes come from HIPE files, so the check is the correctness of the matching.

### UTI_hadx

```{r Check match tables UTI hadx code}
##################################################
# UTI
#
ctable(H.UTI_hadx <- as_factor(Cost2Care.HIPE$H.UTI_hadx),
  uti.hadx <- as_factor(Cost2Care.HIPE$uti.hadx),
  chisq = TRUE,
  prop = "n")

```

### DL_hadx

```{r Check match tables DL hadx code}
##################################################
# DL
#
ctable(H.DL_hadx <- as_factor(Cost2Care.HIPE$H.DL_hadx),
  delirium.hadx <- as_factor(Cost2Care.HIPE$delirium.hadx),
  chisq = TRUE,
  prop = "n")

```

### PU_hadx

```{r Check match tables PU hadx code}
##################################################
# PU
#
ctable(H.PU_hadx <- as_factor(Cost2Care.HIPE$H.PU_hadx),
  pressure.ulcer.hadx <- as_factor(Cost2Care.HIPE$pressure.ulcer.hadx),
  chisq = TRUE,
  prop = "n")

```

### PN_hadx

```{r Check match tables PN hadx code}
##################################################
# PN
#
ctable(H.PN_hadx <- as_factor(Cost2Care.HIPE$H.PN_hadx),
  pneumonia.hadx <- as_factor(Cost2Care.HIPE$pneumonia.hadx),
  chisq = TRUE,
  prop = "n")

```

## There are a couple of anyf2m variable floating about - can we check which is which? I think h.any_f2m comes from the chart review, and h.any_f2m.hadx comes from HIPE?

```{r Check match tables any failure to Maintain (F2M)}
##################################################
# any_F2M
#
#Check
#names(Cost2Care.HIPE)[which(str_detect(names(Cost2Care.HIPE),"hadx"))]
#
ctable(H.any_F2M_hadx <- as_factor(Cost2Care.HIPE$H.any_F2M_hadx),
  any.f2m.hadx <- as_factor(Cost2Care.HIPE$any.f2m.hadx),
  chisq = TRUE,
  prop = "n")

```

## Chart review vs. HIPE

In the second group, one code comes from the chart review, and the other from HIPE. This is the more substantively interesting

### Sex

```{r Check match tables Sex}
##################################################
# Sex
#
ctable(sex <- as_factor(
  Cost2Care.HIPE$sex),
  Cost2Care.HIPE$Gender,
  chisq = TRUE,
  prop = "n")

```

### Age

```{r Check match tables Age}
##################################################
# Age
#
freq(Cost2Care.HIPE$Age_discharge - Cost2Care.HIPE$age) # Mostly ok, i.e. 0, but a few large discrepancies

```

### Elective or emergency admission

```{r Check match tables Elective or emergency admission}
##################################################
# elective or emergency admission
#
ctable(Cost2Care.HIPE$Elective_emergency,
  Cost2Care.HIPE$elem,
  chisq = TRUE,
  prop = "n")

```

### ITU use

```{r Check match tables ITU use}
##################################################
# icu
#
ctable(itulos <- as_factor(Cost2Care.HIPE$itulos),
  Cost2Care.HIPE$ICU,
  chisq = TRUE,
  prop = "n")

```

###  PN

```{r Check match tables Pneumonia}
##################################################
# PN
#
ctable(PN <- as_factor(Cost2Care.HIPE$PN),
  pneumonia <- as_factor(Cost2Care.HIPE$pneumonia),
  chisq = TRUE,
  prop = "n")

```

### UTI

```{r Check match tables UTI}
##################################################
# UTI
#
ctable(UTI <- as_factor(Cost2Care.HIPE$UTI),
  uti <- as_factor(Cost2Care.HIPE$uti))

```

### PU

```{r Check match tables Pressure ulcer}
##################################################
# PU
#
ctable(PU <- as_factor(Cost2Care.HIPE$PU),
  pressure.ulcer <- as_factor(Cost2Care.HIPE$pressure.ulcer))

```

### DL

```{r Check match tables Delirium}
##################################################
# DL
#
ctable(DL <- as_factor(Cost2Care.HIPE$DL),
  delirium <- as_factor(Cost2Care.HIPE$delirium))

```

### Any F2M

```{r Check match tables Any F2M}
##################################################
# any_2FM
#
#Check
#names(Cost2Care.HIPE)[which(str_detect(names(Cost2Care.HIPE),"hadx"))]
#
ctable(H.any_F2M <- as_factor(Cost2Care.HIPE$H.any_F2M),
  any.f2m <- as_factor(Cost2Care.HIPE$any.f2m))

```

```{r Pictures}
ggplot(data=Cost2Care.HIPE,
       aes(x = Age_discharge, y = age, colour=Gender)) + geom_jitter() # A bit clearer

```

# Major outcomes

The main outcomes available are 
* the presence of a health care associated urinary tract infection (UTI - variable beginning with 'UTI.')
* the presence of health care associated pneumonia (PN - variable beginning with 'PN.')
* the presence of a health care associated pressure ulcer (PU - variable beginning with 'PU.')
* the presence of health care associated delirium infection (DL - variable beginning with 'DL.')
* Death recorded
* Prolonged length of stay

It is wholly possible to have several of these outcomes.


# Save files

```{r Save the files}
saveRDS(Cost2Care.HIPE, file = "data/Cost2Care.Hipe.rds",
        ascii = FALSE, version = NULL,
        compress = TRUE, refhook = NULL)
```
