---
title: "Models_scribbles"
author: "Anthony Staines"
date: "`r Sys.Date()`"
output: html_document
---
File storing some preliminary models

# Preliminary modelling

Quantifying this variability we can use a random effects regression model. This allows the analysis of the effects of hospital type and other variables (fixed effects) and the variability between individual hospitals (random effects). For this preliminary work, the national HIPE data set is used.

Our first set of models looks only at age and sex as predictors of length of stay.

```{r Regression}
#Random intercept models
Model0 <- lm(data=HIPE,
             rawlos ~ age + sex)

Model1 <- lmer(data=HIPE,
             rawlos ~ age + sex +
               (1 | ModelF))

Model2 <- lmer(data=HIPE,
             rawlos ~ age + sex +
               (1 | HospCode))

Model3 <- lmer(data=HIPE,
             rawlos ~ age + sex +
               (1 | HospCode) + (1| ModelF))

Model4 <- lmer(data=HIPE,
             rawlos ~ age + sex +
               (1 | ModelF) +
                (1 | ModelF:HospCode))


tab_model(Model4, Model3, Model2, Model1, Model0, show.p = FALSE)
```

Looking at these results, age and sex have, as expected, significant impacts on length of stay. Hospital model, and, within the five hospital models, individual hospitals, all impact on length of stay.

Taking this as our baseline model, the next step is to fit a range of additional variables, and see how these affect the model. Given the number of observations, these need to be considered carefully.

```{r Model 5 RE for DRG}

Model5 <- lmer(data=HIPE,
             rawlos ~ age + sex +
               (1 | ModelF) +
                (1 | ModelF:HospCode) +
                (1 + sex | drgv.8))

Model6 <- lmer(data=HIPE,
             rawlos ~ age + sex +
                (1 | HospCode) +
                (1 | drgv.8))

tab_model(Model4, Model5, Model6)

```

The DRG code, as one might expect, has a huge impact on the length of stay. Much of the variability associated with hospital type is subsumed into the variability from the DRGs.

```{r Model 6 to 8 test out scores}

Model6 <- lmer(data=HIPE,
             rawlos ~ age + sex + ScoreEl +
               (1 | ModelF) +
                (1 | ModelF:HospCode) +
                (1 | drgv.8))
tab_model(Model6,Model5)

Model7 <- lmer(data=HIPE,
             rawlos ~ age + sex + ScoreCh +
               (1 | ModelF) +
                (1 | ModelF:HospCode) +
                (1 | drgv.8))
tab_model(Model7,Model6, Model5)

Model8 <- lmer(data=HIPE,
             rawlos ~ age + sex + ScoreEl + ScoreCh +
               (1 | ModelF) +
                (1 | ModelF:HospCode) +
                (1 | drgv.8))
tab_model(Model8, Model7, Model6)

```

Either the Elixhauser score, or the Charlson score, is a significant predictor of length of stay, but adding both is superfluous, so we choose to use only the Elixhauser score, as it seems to be more closely linked to our outcome.

```{r Elixhauser score only}
Model9 <- lmer(data=HIPE,
             rawlos ~ age + sex + ScoreEl + Source +
               (1 | ModelF) +
                (1 | ModelF:HospCode) +
                (1 | drgv.8))
tab_model(Model9, Model6)

```

The source of admission is also important. Most are admitted from home, but those admitted from long-term care facilities have shorter lengths of stay, and those transferred from other hospitals have longer lengths of stay.

```{r Add season of admission}
Model10 <- lmer(data=HIPE,
             rawlos ~ age + sex + ScoreEl + Source + SeasonOfAdmission +
               (1 | ModelF) +
                (1 | ModelF:HospCode) +
                (1 | drgv.8))
tab_model(Model10, Model9)

```

Fitting the Season of Discharge (Winter or Other) makes a modest contribution to the length of stay, but it has been identified in other work, so it will be retained.

```{r Add crude medical surgical split}
Model11 <- lmer(data=HIPE,
             rawlos ~ age + sex + ScoreEl + Source + SeasonOfAdmission + MedSurg +
               (1 | ModelF) +
                (1 | ModelF:HospCode) +
                (1 | drgv.8))
tab_model(Model11, Model10, Model9)

```

A rather crude split into medical and surgical cases shows much lower lengths of stay for surgical than medical cases, again as expected.

```{r Add eligibility}
Model12 <- lmer(data=HIPE,
             rawlos ~ age + sex + ScoreEl + Source + SeasonOfAdmission + MedSurg + fullelig +
               (1 | ModelF) +
                (1 | ModelF:HospCode) +
                (1 | drgv.8))
tab_model(Model12, Model11, Model10)

```

Full eligibility increases the length of stay.

```{r Add elective/emergency admission}
Model13 <- lmer(data=HIPE,
             rawlos ~ age + sex + ScoreEl + Source + SeasonOfAdmission + MedSurg + fullelig + elem +
               (1 | ModelF) +
                (1 | ModelF:HospCode) +
                (1 | drgv.8))
tab_model(Model13, Model12, Model11)

```

Emergency admissions stay longer.

```{r table eligibility, elem and MedSurg}

ctable(MedSurg <- as_factor(HIPE$MedSurg),
  elem <- as_factor(HIPE$elem),
  prop = "r")

ctable(MedSurg <- as_factor(HIPE$MedSurg),
  fullelig <- as_factor(HIPE$fullelig),
  prop = "r")
```

There are big differences between medical and surgical cases in terms of eligibility and elective or emergency admissions.

## Linear and non-linear models

These are linear models, with (in principle) unconstrained outputs. This is not quite true, as for example, negative lengths of stay do not occur, there is a long positive tail, and this data set is limited to those with a length of stay of at least three days. However, for our purposes, exploratory modelling these seem at least useful.

To examine deaths, where the outcome variable is binary, Alive or Dead, at the time of discharge, requires non-linear models, and the usual choice is a logistic model.

```{r glmm model, eval = FALSE}

LogModel1 <- glmer(data=HIPE %>%
                     mutate(DiedL = Died == "Dead"),
             DiedL ~ age + sex + ScoreEl + Source + SeasonOfAdmission +
               (1 | ModelF) +
                (1 | ModelF:HospCode) +
                (1 | drgv.8),
             family = binomial,
             control = glmerControl(optimizer = "bobyqa"))

tab_model(LogModel1)
```

While the numerical values are wildly different, and they are odds ratios, the confidence intervals of the parameters, and the size of the random effects remain convincing, suggesting that a similar model will explain deaths quite well too.

# Interpretation

None of this is surprising. Age, gender, and diagnosis (here represented as DRG), are obvious predictors of good and bad outcomes. The hospitals have very different roles, and very different catchment areas, all of which are expected to be relevant to outcomes.

```{r Save the files}
saveRDS(HIPE, file = "data/Hipe.rds",
        ascii = FALSE, version = NULL,
        compress = TRUE, refhook = NULL)
saveRDS(HIPE.Site, file = "data/Hipe.Site.rds",
        ascii = FALSE, version = NULL,
        compress = TRUE, refhook = NULL)
```

# Bibliography


