---
title: "Predictions_Outcomes_ranger.Rmd"
author: "Anthony Staines"
date: "`r Sys.Date()`"
output: html_document
---

```{r clean up environment}
rm(list = ls())
```

# Intent

Our aim is to develop models for prediction of the various adverse outcomes, pneumonia, UTI, delirium and pressure ulcer from HIPE data. There are two HIPE data sets, one for all the HIPE data (H.N) and one for HIPE data from the chart review site (H.S). The gold standard for complications these is the chart review data (CTC.H).

The most obvious limitation is that the chart review was done in one hospital, a model 4 centre. The national HIPE data used here has only Model 3 and Model 4 hospitals.

# Predictions

Prepares predictions for each of our outcomes using a tree-based (ranger) classification approach, for the study site file, using the study (chart review) outcomes, and the HIPE predictors. These are then applied to the national data to see how they perform.

```{r setup, include=FALSE}
#####################################################
#Load libraries
library(tidyverse)
library(knitr)
library(kableExtra)
library(patchwork)

library(ranger)
library(mlr3verse)
library(mlr3viz)
library(data.table)

library(future)

#####################################################
# Set up knitr
knitr::opts_chunk$set(echo = FALSE, cache = TRUE, warning = NA, message = NA, fig.pos = 'H',
      cache.extra = knitr::rand_seed)

#####################################################
#How many CPU's?
N = 16
  options(Ncpus = N - 1)
  options(mc.cores = N - 1)
  setDTthreads(threads = N - 1,
               restore_after_fork = TRUE,
               throttle = 1024)

options(dplyr.summarise.inform = FALSE, # shut up summarise
        ranger.num.threads = N) # Prepare for rf models

#####################################################
# Set logger for mlr3
lgr::get_logger("mlr3")$set_threshold("error")
lgr::get_logger("bbotk")$set_threshold("error")

#####################################################
# Set random seed
set.seed(979)

#####################################################
# Tidy up
rm(N)
```

## Load the merged data file, and the national file
These are the chart review file merged with the matched HIPE file provided by HPO, and the national HIPE file. They have been extensively processed.

```{r Load data file}
#####################################################
# Load the merged HIPE/Study data file
# 
CTC.H <- readRDS('data/transformed_data/CTC.H.Rds')

#####################################################
# Load the total national HIPE data file
# 
H.N <- readRDS('data/transformed_data/H.N.Rds')

```

## Tidy loaded data

```{r Remove non-HIPE codes, except for outcomes, and duplicate codes}
#####################################################
#
    CTC.H <- CTC.H %>%
    select(-c("StudyID", "Gender_consensus",
              "Age_consensus", "AgeC",
              "Elective_Emergency", "discode","source",
              "Ward_moves", "Bed_moves",
              "hosp.anon", "HospNo", "ModelF")) %>%
        select(-c("healthins.g")) # Mostly missing
```

## Proportions of each adverse outcome

```{r Proportions of each adverse outcome}
#####################################################
#
Proportions <- CTC.H |>
  select(PN:F2M, Died) |>
  mutate(across(PN:Died,
                ~ fct_count(as_factor(.),
                            prop=TRUE)$p[[2]])) |> # Proportion of Yes for each adverse Outcome (the smaller proportion)
  unique()
```

These are the percentage of chart reviews in which an adverse event was identified.

```{r Table of percentage of adverse events in chart review, results='asis'}
#####################################################
#
Proportions |>
  mutate(across(everything(), ~(round(. * 100,2)))) |>
  kable(caption = 'Percentage of people from chart review  experiencing each adverse outcome')

```

The commonest adverse event was 'Failure to maintain'. The goal of this work is to predict these adverse outcomes.

# Configuration

These functions set up the set of measures to be considered, and the resampling approach used (initially 10-fold cross-validation).

## Define desired measures

```{r Define measures}
Set_measures <- function(){
Measures = msrs(
    c('classif.auc','classif.bbrier',
      'classif.logloss','classif.acc'))
return(Measures)
}
```

## Define resampling approach

```{r Define resampling approach}
#
# Define resampling approach
#  
Set_resampling <- function(){
  cv10 = rsmp("cv", folds = 10) # 10 folds cross-validation
return(cv10)
}
```

# Assistive functions for analysis

These are a set of functions used to make the modelling simpler

## select columns given the colunn name

```{r Function to select columns by name}
##################################################################
# This function allows us to replace a given outcome (PN etc...)
#  with the generic variable Outcome. Hence we can model Outcome
#  without worrying about which Outcome we've got
#
Set_Outcome <- function(Outcome = PN, df = CTC.H ) {
    df |>
        mutate(Outcome = {{Outcome}})
}

# Check
Df <- Set_Outcome(PN,CTC.H)
    table(Df$PN,Df$Outcome)
Df <- Set_Outcome(UTI,CTC.H)
    table(Df$UTI,Df$Outcome)
Df <- Set_Outcome(PU,CTC.H)
    table(Df$PU,Df$Outcome)
Df <- Set_Outcome(DL,CTC.H)
    table(Df$DL,Df$Outcome)
Df <- Set_Outcome(F2M,CTC.H)
    table(Df$F2M,Df$Outcome)
# All passed    
rm(Df)
```

# Task

## Define an outcome task

This defines the key task for analysis. It is a classification task, with Weights used, and the positive value set to 'Yes'.

```{r function to set up task}
# Set up task
##################################################
# Define a classification task for Outcome (PN:F2M).
#
Set_task <- function(Outcome = Outcome,
                     Data_for_classification = Df){
  
  tsk_Outcome <- as_task_classif(Data_for_classification,
                    target = "Outcome",
                    id = "Outcome",
                    positive = "Yes", # Makes 'Yes' the rarer outcome, the positive response
                  )

  tsk_Outcome$col_roles$weights_learner = "Weights"
  tsk_Outcome$select(
    setdiff(tsk_Outcome$feature_names, "Weights")) # Remove Weights as a feature

return(tsk_Outcome)
}
```

### plot task

This function allows you to draw the task as a histogram.

```{r function to plot task}

plot_task <- function(tsk_Outcome) {
  autoplot(tsk_Outcome) + 
    labs (title = 'Outcome',
          x = 'Outcome',
          y = 'Coding in chart review')
}
```

## Importance

We calculate the permutation importance for classification of each variable provided in a given task. This used later to filter the data.

### Calculate importance

This calculates and returns the importance of the variables in a task,

```{r function to calculate importance}
importance <- function(task) {
  lrn_Filter = lrn("classif.ranger",
                 seed = 42)
  lrn_Filter$param_set$values = list(importance = "permutation")
  
  flt_Imp = flt("importance", learner = lrn_Filter)
  IMPORTANCE <- flt_Imp$calculate(task)
}
```

### filter by importance

This allows to filter the data in a task, given the precalculated importance. It is set up to filter by quantiles of importance. In the first case it is the 5th centile (p = 1/20) of the importance values greater than 0.

```{r function to filter by importance}
filter_importance <- function(tsk, importance, P = 1/20) {
  t_Imp <- tibble(as.data.table(importance))

# Produces a single number for a cutoff
  Q <- t_Imp %>%
    filter(score > 0) %>%
    summarise(Q = quantile(score,P)) %>% 
    as.numeric()
  
  t_Imp <- t_Imp %>% filter(score > Q)
    keep = t_Imp$feature
      tsk$select(keep)

return(tsk)
}
```

### draw importance

Produces and draws a nice graph of importance.

```{r function to draw importance}
draw_importance <- function(Importance,
                            Outcome_label = "Outcome",
                            cut_off = "0"){
Title <-  paste0("Plot of importance by feature for ",
                   Outcome_label)
Subtitle <- paste0("Importance greater than ", cut_off)

Importance.df <-
    setDF(as.data.table(Importance)) |>
    filter(score > 0) |>
    arrange(desc(score), feature) |>
    mutate(featureF = factor(feature)) |>
    mutate(featureF = fct_reorder(featureF, score))

ggplot(Importance.df, aes(x = score, y = featureF)) +
  geom_point(colour = 'red') +
  labs(title = Title, subtitle = Subtitle,
       x = "Permutation importance", y = "Feature") +
  theme_minimal()
  }
```

## Training and prediction

### simple trainer

Works on the training data to create a trainer.

```{r function for simple trainer}
trainer <- function(tsk_Outcome, split_Outcome,
                    mtry = 12, num.trees = 2000){
  Mtry = mtry
  Num.Trees = num.trees
  
  # Define a learning task
  lrn_Outcome = lrn('classif.ranger',
            predict_type = "prob",
            mtry = Mtry,
            num.trees = Num.Trees,
            importance = "permutation")

# Learn from the training data
  lrn_Outcome$train(tsk_Outcome,split_Outcome$train)

return(lrn_Outcome)
}
```

### make predictions

```{r function to run predictions}
predict_tsk <- function(tsk, data) {

# Predict from the test data
  prediction = lrn_Outcome$predict(tsk_Outcome,
                              split_Outcome$test)
return(prediction)
}
```

### print predictions

```{r function to print selected prediction output}
#
## function for simple trainer measures printing
# 
print_predictions <- function(prediction) {
  cat("AUC ","BBrier ","LogLoss ","Accuracy","\n")
  cat(round(prediction$score(Measures),3),"\n")
}
```

### summarise prediction
summarise_prediction <- function(prediction){

}

## Tuning
###Tune trainer for mtry and num.trees

```{r function to tune trainer}
tune_trainer <- function(tsk_Outcome = tsk_Outcome,
                         n_Evaluations = 500,
                         measures = Measures,
                         cv = cv10){
  search_space = ps(
    mtry = p_int(lower = 3, upper = 13),
    num.trees = p_int(900, 2000)
  )

  lrn_Outcome = lrn('classif.ranger',
            predict_type = "prob",
            importance = "permutation"
            )

  glrn_Outcome = GraphLearner$new(lrn_Outcome)

  instance_Outcome = ti(
    task = tsk_Outcome,
    learner = glrn_Outcome,
    resampling = cv10,
    terminator = trm("evals",
                   n_evals = n_Evaluations), # For tuner "random_search"
    search_space = search_space,
    measures = Measures
  )
cat("Tuner reached")
tuner = tnr("random_search")
  future::plan(multisession, workers = 10)

tuner$optimize(instance_Outcome)

Tuner_df <- as_tibble(
  as.data.table(instance_Outcome$archive))

Tuner_df
}
```

### graph tuner results

```{r Draw tuners}
draw_tuners = function(Tuner_df,
                       TITLE = 'TITLE',
                       Threshold = 0.5){
  # mtry
    #Maximise
    AUC.m <- ggplot(data = Tuner_df,
          aes(x = mtry,
              y = classif.auc)) +
        geom_smooth(colour = 'red') +
      theme_minimal()
    #Minimise
    BBRIER.m <- ggplot(data = Tuner_df,
                 aes(x = mtry,
                     y = classif.bbrier)) +
        geom_smooth(colour = 'green') +
      scale_y_reverse() +
      theme_minimal()
    #Maximise
    ACC.m <- ggplot(data = Tuner_df,
              aes(x = mtry,
                  y = classif.acc)) +
        geom_smooth(colour = 'red') +
      theme_minimal()
    #Minimise
    LOGLOSS.m <- ggplot(data = Tuner_df,
                  aes(x = mtry,
                      y = classif.logloss)) +
        geom_smooth(colour = 'green') +
      scale_y_reverse() +
      theme_minimal()

  # num.trees
    #Maximise
    AUC.t <- ggplot(data = Tuner_df,
          aes(x = num.trees,
              y = classif.auc)) +
        geom_smooth(colour = 'red') +
      theme_minimal()
    #Minimise
    BBRIER.t <- ggplot(data = Tuner_df,
                 aes(x = num.trees,
                     y = classif.bbrier)) +
        geom_smooth(colour = 'green') +
      scale_y_reverse() +
      theme_minimal()
    #Maximise
    ACC.t <- ggplot(data = Tuner_df,
              aes(x = num.trees,
                  y = classif.acc)) +
        geom_smooth(colour = 'red') +
      theme_minimal()
    #Minimise
    LOGLOSS.t <- ggplot(data = Tuner_df,
                  aes(x = num.trees,
                      y = classif.logloss)) +
        geom_smooth(colour = 'green') +
      scale_y_reverse() +
      theme_minimal()
    IMAGE <- AUC.m + AUC.t +
      BBRIER.m + BBRIER.t +
      ACC.m+ ACC.t +
      LOGLOSS.m + LOGLOSS.t +
        plot_annotation(title = TITLE) +
        plot_annotation(subtitle = cat("Threshold is ", Threshold)) +
        plot_layout(axis_titles = 'collect') +
      plot_layout(nrow = 4)
      
return(IMAGE)
}

```

## Threshold for classification

### select optimum threshold

```{r Function to calculate optimum threshold}
Set_Threshold <- function(df) {
  df <- df %>%
    rowid_to_column(var = 'Threshold') %>%
    mutate(Threshold = Threshold/n()) %>%
    mutate(Specificity =  1 - x) %>%
    mutate(Sensitivity = y) %>%
    mutate(Diff = Sensitivity - Specificity) %>%
      slice(which.min(abs(Diff))) %>%
  select(Threshold)
    
return(df)
}
```

# Set up configuration

Set up the resampling strategy and the set of measures to be reported on.

```{r Set up configuration}
  cv10 <- Set_resampling()

  Measures <- Set_measures()

```

# Outcomes
## Set Outcome to "PN"

```{r Outcome = PN}
Df <- Set_Outcome(PN,CTC.H)
    table(Df$PN,Df$Outcome)
    Short_label <- 'PN'
    Full_label <- 'PN - pneumonia'
```

```{r Set up and stratify task and split}

# Remove all outcomes, except the desired one
Df <- Df |> select(-c(PN:F2M))

# Set up task
tsk_Outcome <- Set_task(Outcome, Df)
  split_Outcome <- mlr3::partition(tsk_Outcome)
      tsk_Outcome
          split_Outcome

    plot_task(tsk_Outcome)

    lrn_Outcome <- trainer(tsk_Outcome, split_Outcome)
      lrn_Outcome$model

    IMPORT <- importance(tsk_Outcome)
      draw_importance(Importance = IMPORT,
                Outcome_label = Short_label,
                cut_off = 0)

    prediction_train <-
      lrn_Outcome$predict(tsk_Outcome,
                        split_Outcome$train)
    prediction_test <-
      lrn_Outcome$predict(tsk_Outcome,
                        split_Outcome$test)

    prediction_train$score(Measures)
    prediction_test$score(Measures)

      tsk_Outcome_f <- filter_importance(tsk_Outcome,
                        IMPORT, P=1/10)
      IMPORT_f <- importance(tsk_Outcome_f)
        draw_importance(Importance = IMPORT_f,
                Outcome_label = Short_label,
                cut_off = "10th centile")
        
    lrn_Outcome_f <- trainer(
      tsk_Outcome_f, split_Outcome)
      lrn_Outcome_f$model

    prediction_train_f <-
      lrn_Outcome_f$predict(tsk_Outcome_f,
                        split_Outcome$train)
    prediction_test_f <-
      lrn_Outcome_f$predict(tsk_Outcome_f,
                        split_Outcome$test)
    prediction_train_f$score(Measures)
    prediction_test_f$score(Measures)

```    

```{r Print and plot predictions}

roc_outcome_1 = autoplot(prediction_test, type = 'roc') +
    labs(title = Full_label,
         subtitle = 
           paste0('Full - AUC is ',
            round(prediction_test$score(
              msr('classif.auc')),3))
         ) ; roc_outcome_1
roc_outcome_2 = autoplot(prediction_test_f, type = 'roc') +
    labs(title = Full_label,
         subtitle = paste0('Filtered - AUC is ',
            round(prediction_test_f$score(
              msr('classif.auc')),3))
         ) ; roc_outcome_2
```

```{set Threshold}
  Threshold_optimised_1 =as.numeric(
    Set_Threshold(roc_outcome_1$data))
  Threshold_optimised_2 =as.numeric(
    Set_Threshold(roc_outcome_2$data))
  
  prediction_train$set_threshold(Threshold_optimised_1)
  prediction_test$set_threshold(Threshold_optimised_1)

    prediction_train$score(Measures)
    prediction_test$score(Measures)

  prediction_train_f$set_threshold(Threshold_optimised_2)
  prediction_test_f$set_threshold(Threshold_optimised_2)

    prediction_train_f$score(Measures)
    prediction_test_f$score(Measures)
```

```{r Tuning}
tune_df_1 <- tune_trainer(tsk_Outcome, 50)
  draw_tuners(tune_df_1, TITLE = Full_label)
tune_df_2 <- tune_trainer(tsk_Outcome_f, 50)
  draw_tuners(tune_df_2, TITLE = Full_label)

```

From inspection of the graphs, it looks as if the outcomes are relatively insensitive to tree depth (mtry) and the number of trees analysed (num.tree).
It looks if between 5 and 10 is the best value for mtry, so we pick 8; similarly the best range for num.trees is about 1,100 to 1,300, so we pick 1,200. The optimum cutoff for the threshold seems to be about `r round(Threshold_optimised, 2)`, rather than the default of 0.5.

```{r run final prediction set}
set.seed(989)
#
# Keep original version of tsk_Outcome
#
tsk_Hold <- tsk_Outcome$clone()
#

rr_Outcome_1 <- resample(
  task = tsk_Outcome$filter(split_Outcome$train),
  learner = lrn_Outcome,
  resampling = cv10,
  store_models = TRUE,
  store_backends = TRUE)

tsk_Outcome$data()
rr_Outcome_1$prediction()

rr_Outcome_2 <- resample(
  task = tsk_Outcome_f$filter(split_Outcome$train),
  learner = lrn_Outcome_f,
  resampling = cv10,
  store_models = TRUE,
  store_backends = TRUE)

tsk_Outcome_f$data()
rr_Outcome_2$prediction()

  rr_Outcome_1$aggregate(Measures)
  rr_Outcome_2$aggregate(Measures)

autoplot(rr_Outcome_1, type = 'roc') +
  labs(title = Full_label,
       subtitle = paste0('Full - AUC is ',
       round(rr_Outcome_1$aggregate(
           msr('classif.auc')),3))) +
autoplot(rr_Outcome_2, type = 'roc') +
  labs(title = Full_label,
              subtitle = paste0('Full - AUC is ',
       round(rr_Outcome_2$aggregate(
           msr('classif.auc')),3))) +
  plot_annotation(title = 'Resampled ROC curves for full and filtered data')

####################################
# Predictions
#
L1  <- rr_Outcome_1$learners[[1]]
L2  <- rr_Outcome_2$learners[[1]]


tsk_Hold_all <- tsk_Hold$clone()      
L1_all <- L1$predict_newdata(newdata =
                  as_tibble(
                    tsk_Hold_all$data()),
                  task = tsk_Outcome)

L1_all

tsk_Hold_train <- tsk_Hold$clone()
L1_train <- L1$predict_newdata(newdata =
                  as_tibble(
              tsk_Hold_train$filter(
                split_Outcome$train)$data()),
                  task = tsk_Outcome)
L1_train

tsk_Hold_test <- tsk_Hold$clone()
L1_test <- L1$predict_newdata(newdata =
                  as_tibble(
                    tsk_Hold_test$filter(
                      split_Outcome$test)$data()),
                  task = tsk_Outcome)
L1_test

L1_all$score(Measures)
L1_train$score(Measures)
L1_test$score(Measures)

L1_all
L1_train
L1_test
```



```{r Predict for HIPE}
L1$predict_newdata(newdata = H.N,
                      task = tsk_Outcome)


L1$predict_newdata(newdata = H.N,
                      task = tsk_Outcome_tr %>% filter)


Lfull$predict_newdata(newdata = H.N,
                      task = tsk_Outcome)
```


# UTI

```{r Outcome = UTI}
Df <- Set_Outcome(UTI,CTC.H)
    table(Df$UTI,Df$Outcome)
```

```{r Set up and stratify task and split}
```

# PU

```{r Outcome = PU}
Df <- Set_Outcome(PU,CTC.H)
    table(Df$PU,Df$Outcome)
```

```{r Set up and stratify task and split}
```

# DL

```{r Outcome = DL}
Df <- Set_Outcome(DL,CTC.H)
    table(Df$DL,Df$Outcome)
```

```{r Set up and stratify task and split}
```

# F2M

```{r Outcome = F2M}
Df <- Set_Outcome(F2M,CTC.H)
    table(Df$F2M,Df$Outcome)
```

```{r Set up and stratify task and split}

```
